Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-06-11 manuscript.Rmd
Trying to fix OSF download of headerfile
Trying to sort OSF auto downloading
Added small resource files to a new directory in the repository so they don't need to be downloaded from OSF

>>>>

if (!file.exists(paste0(datadir,'headerfile.csv'))){
# copy from resources folder
file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
}

if (!file.exists(paste0(localdir,'StimulusExample.png'))){
# copy from resources folder
file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
}
